### 2024-08-16 manuscript.tex
Figure improvements

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\setsansfont{Source Sans Pro}
\setmainfont{Source Serif Pro}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Using ship observations to assess Southern Ocean clouds in a storm-resolving general circulation model ICON},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}
%\renewcommand{\bibsection}{\section*{Publications}}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Using ship observations to assess Southern Ocean clouds in the storm-resolving general circulation model ICON}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, New Zealand\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{img/cl_agg.pdf}
\caption{
Cloud occurrence by height calculated as the average of all voyages and stations
for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
the set of all voyages and stations. The subsets \textbf{(a--g)} are described
in the text (Section \ref{sec:results}).}
\label{fig:cloud-occurrence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{img/radiosonde.pdf}
\caption{Radiosonde proﬁles of potential temperature and lifting condensation
level (LCL) on all RV \emph{Polarstern} voyages.}
\label{fig:radiosonde}
\end{figure}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\setsansfont{Source Sans Pro}
\setmainfont{Source Serif Pro}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}
%\renewcommand{\bibsection}{\section*{Publications}}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, New Zealand\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cl_agg_exp.pdf}
\caption{
Cloud occurrence by height calculated as the average of all voyages and stations
for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
the set of all voyages and stations. The subsets \textbf{(a--g)} are described
in the text (Section \ref{sec:results}).}
\label{fig:cloud-occurrence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
\caption{
Virtual potential temperature ($\theta_v$) and relative humidity (RH)
determined from radiosonde launches and co-located profiles in
ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
The solid lines are the average calculated from the averages of every
individual voyage and station. The bands span the
16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
of the voyage and station averages.
}
\label{fig:theta-hur}
\end{figure}
